### 2024-04-30 assets/viva/riscatter.tex
:construction: Add viva slides

\begin{tikzpicture}[every node/.style={draw,ultra thick},every path/.style={ultra thick},every text node part/.style={align=center}]
	\node at (0,0) [circular sector,shape border rotate=90,minimum width=2cm] {};
	\node at (5,3) [circle,minimum size=1.25cm] {};
	\node at (8,0.55) [circular sector,shape border rotate=270,minimum width=2cm] {};

@@

	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (1,-0.25) -- (7.375,-0.25);
	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (0.5,0.75) -- (4,3);
	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (6,3.1625) -- (8,1.25);
	\draw[green,decorate,decoration={crosses,segment length=8mm,shape size=1.5mm}] (6.29,2.885) -- (8,1.25);

>>>>

\begin{tikzpicture}[font=\LARGE,every node/.style={draw,ultra thick},every path/.style={ultra thick},every text node part/.style={align=center}]
	\node at (0,0) [circular sector,shape border rotate=90,minimum width=2cm] {};
	\node at (5,3) [circle,minimum size=1.25cm] {};
	\node at (8,0.55) [circular sector,shape border rotate=270,minimum width=2cm] {};

@@

	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (1,-0.25) -- (7.375,-0.25);
	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (0.5,0.75) -- (4,3);
	\draw[blue,decorate,decoration={waves,segment length=4mm,radius=2mm}] (6,3.1625) -- (8,1.25);
	\draw[orange,decorate,decoration={crosses,segment length=8mm,shape size=1.5mm}] (6.29,2.885) -- (8,1.25);

### 2024-04-30 assets/viva/wpt_architecture.tex
:construction: Add viva slides

\begin{circuitikz}[transform shape,align=center,font=\footnotesize]
	\draw(0,0) node[draw](rf){\gls{rf}\\source};
	\draw(rf.east) node[txantenna]{};
	\draw(1,1) node{Tx};
	\draw(4.875,2) node[draw]{\gls{ris}};
	\draw(4.875,1) node[draw]{Channel};
	\draw(10,0) node[draw](mc){Matching\\network};
	\draw(mc.west) node[rxantenna,xscale=-1]{};
	\draw(8.7,1) node{Rx};
	\draw(mc.east) to ++(0.85,0) node[anchor=west,draw](d){Diode};
	\draw(d.east) to ++(0.85,0) node[anchor=west,draw](lpf){Low-pass\\filter};
	\draw(lpf.east) to ++(1,0) node[anchor=west,draw](dd){\gls{dc}-\gls{dc}\\converter};
	\draw(dd.east) to ++(1,0) node[anchor=west,draw](s){Storage};

	\draw [dashed] (-0.95,-0.75) rectangle (3.75,2.75);
	\draw (1.4,3) node[]{Energy transmitter};
	\draw [dotted] (6.25,-0.5) rectangle (15.6,2.5);
	\draw (10.925,2) node[]{Rectenna};
	\draw [dotted] (16,-0.5) rectangle (20.5,1.25);
	\draw (18.25,0.875) node[]{Power management unit};
	\draw [dashed] (6,-0.75) rectangle (20.75,2.75);
	\draw (13.375,3) node[]{Energy receiver};

	\draw (-0.95,-1) node[]{$P_{\mathrm{DC}}^{\mathrm{T}}$};
	\draw (3.75,-1) node[]{$P_{\mathrm{RF}}^{\mathrm{T}}$};
	\draw (6,-1) node[]{$P_{\mathrm{RF}}^{\mathrm{R}}$};
	\draw (15.8,-1) node[]{$P_{\mathrm{DC}}^{\mathrm{R}}$};
	\draw (20.5,-1) node[]{$P_{\mathrm{DC}}^{\mathrm{S}}$};

>>>>

\begin{circuitikz}[transform shape,align=center]
	\draw(0,0) node[draw](rf){\gls{rf}\\source};
	\draw(rf.east) node[txantenna]{};
	\draw(1,1) node{Tx};
	\draw(4.875,2) node[draw]{\textcolor{orange}{\gls{ris}}};
	\draw(4.875,1) node[draw]{\textcolor{orange}{Channel}};
	\draw(10,0) node[draw](mc){Matching\\network};
	\draw(mc.west) node[rxantenna,xscale=-1]{};
	\draw(8.7,1) node{Rx};
	\draw(mc.east) to ++(0.85,0) node[anchor=west,draw](r){\textcolor{blue}{Rectifier}};
	% \draw(d.east) to ++(0.85,0) node[anchor=west,draw](r){Low-pass\\filter};
	\draw(r.east) to ++(1,0) node[anchor=west,draw](dd){\gls{dc}-\gls{dc}\\converter};
	\draw(dd.east) to ++(1,0) node[anchor=west,draw](s){Storage};

	\draw [dashed] (-0.95,-0.75) rectangle (3.75,2.75);
	\draw (1.4,3) node[]{Energy transmitter};
	\draw [dotted] (6.25,-0.5) rectangle (13.2,2.5);
	\draw (9.9,2) node[]{\textcolor{blue}{Rectenna}};
	\draw [dotted] (13.8,-0.5) rectangle (19.9,1.25);
	\draw (16.75,0.875) node[]{Power management unit};
	\draw [dashed] (6,-0.75) rectangle (20.1,2.75);
	\draw (13.375,3) node[]{Energy receiver};

	\draw (-0.95,-1) node[]{$P_{\mathrm{DC}}^{\mathrm{T}}$};
	\draw (3.75,-1) node[]{$P_{\mathrm{RF}}^{\mathrm{T}}$};
	\draw (6,-1) node[]{$P_{\mathrm{RF}}^{\mathrm{R}}$};
	\draw (13.5,-1) node[]{$P_{\mathrm{DC}}^{\mathrm{R}}$};
	\draw (20.3,-1) node[]{$P_{\mathrm{DC}}^{\mathrm{S}}$};
